Capstone Movielens Report

### 2025-02-03 reports/capstone-movielens-report.Rmd
Fix for Rmd report.

The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
Following the _Netflix Grand Prize Contest_[@NYT1MNP] requirements, we will evaluate the RMSE score defined as[@IDS2_23-2]:

>>>>

The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
Following the [Netflix Grand Prize Contest](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/index.html) requirements, we will evaluate the RMSE score defined as:

### 2025-02-03 reports/capstone-movielens-report.pdf-template.Rmd
Fix for Rmd report.

The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
Following the _Netflix Grand Prize Contest_[@NYT1MNP] requirements, we will evaluate the RMSE score defined as:

>>>>

The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
Following the [Netflix Grand Prize Contest](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/index.html) requirements, we will evaluate the RMSE score defined as:
